On the properties of discs around accreting brown dwarfs

### 2010-06-25 BDD_submit/paper.tex
Equilibrium misspelt in abstract
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2320 25464f21-6099-402c-b30a-640f1d40d38b

  We present a grid of models of accreting brown dwarf systems with
  circumstellar discs. The calculations involve a self-consistent
  solution of both vertical hydrostatic and radiative equilibirum
  along with a sophisticated treatment of dust sublimation. We have
  simulated observations of the spectral energy distributions and
  several broadband photometric systems. Analysis of the disc
  structures and simulated observations reveal a natural dichotomy in
  accretion rates, with \logmdot $>-$9 and $\leq -$9 classed as
  extreme and typical accretors respectively.  Derivation of ages and
  masses from our simulated photometry using isochrones is demostrated
  to be unreliable even for typical accretors. Although current brown
  dwarf disc candidate selection criteria have been shown to be
  largely reliable when applied to our model grid we suggest improved
  selection criteria in several colour indices. We show that as
  accretion rates increase brown dwarf disc systems are less likely to
  be correctly identified. This suggests that, within our grid,
  systems with higher accretion rates would be preferentially lost
  during brown dwarf target selection. We suggest that observations
  used to assert a $\dot{M}\propto M_*^2$ relationship may
  contain an intrinsic selection bias.

>>>>

  We present a grid of models of accreting brown dwarf systems with
  circumstellar discs. The calculations involve a self-consistent
  solution of both vertical hydrostatic and radiative equilibrium
  along with a sophisticated treatment of dust sublimation. We have
  simulated observations of the spectral energy distributions and
  several broadband photometric systems. Analysis of the disc
  structures and simulated observations reveal a natural dichotomy in
  accretion rates, with \logmdot $>-$9 and $\leq -$9 classed as
  extreme and typical accretors respectively.  Derivation of ages and
  masses from our simulated photometry using isochrones is demostrated
  to be unreliable even for typical accretors. Although current brown
  dwarf disc candidate selection criteria have been shown to be
  largely reliable when applied to our model grid we suggest improved
  selection criteria in several colour indices. We show that as
  accretion rates increase brown dwarf disc systems are less likely to
  be correctly identified. This suggests that, within our grid,
  systems with higher accretion rates would be preferentially lost
  during brown dwarf target selection. We suggest that observations
  used to assert a $\dot{M}\propto M_*^2$ relationship may contain an
  intrinsic selection bias.
